---
title: "Technocolour"
author:
  - "Sophie Meakin"
date: "`r Sys.Date()`"
output:
  md_document:
    variant: markdown_github
    toc: true
    toc_depth: 1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

devtools::load_all()
```

# technocolor

The technocolor package contains colour palettes based on the album artwork some of my
favourite electronic music records. The name "technocolour" is a slight misnomer since they're not all techno records - apologies. 

## Installation

```{r, eval = FALSE}
devtools::install_github("sophiemeakin/technocolour")
```

## Usage

The `technocolours()` function makes a discrete colour palette based on
your chosen track, specified with `name = "track_name"`. The option `n` allows you to specify the number of colours in the palette, which is 6 by default.

## Palettes

```{r}
print_palette(name = "esther")
print_palette(name = "fluorescent_rush")
print_palette(name = "glue")
print_palette(name = "hot_bot")
print_palette(name = "ibrik")
print_palette(name = "poodle_power")
```

## Palette info

The function `info()` prints the name of the track, artist and a URL to the song.

```{r}
info("fluorescent_rush")
```
