---
title: "Technocolour"
author:
  - "Sophie Meakin"
date: "`r Sys.Date()`"
output:
  md_document:
    variant: markdown_github
    toc: false
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE,
                      fig.path = "man/figures/")

library(ggplot2)
devtools::load_all()

```

# technocolour: colour palettes based on electronic music records

The `technocolour` package contains colour palettes based on the album artwork some of my favourite electronic music records. Enjoy!

## Installation

```{r, eval = FALSE}
devtools::install_github("sophiemeakin/technocolour")
```

## Usage

The `technocolours()` function makes discrete and continuous colour palettes based on electronic music records, specified with `name = "track_name"`.

### Examples

```{r example1, fig.width = 12, fig.height = 6, dpi = 400}

ggplot(data = iris,
       aes(x = Petal.Length, y = Petal.Width, col = Species)) +
  geom_point(size = 3) +
  scale_color_techno(name = "rush") +
  theme_bw() +
  theme(legend.position = "top",
        text = element_text(size = 14))

```

### Availble palettes

List the names of all available palettes with `list_palettes()`:

```{r}
list_palettes()
```

### Visualise palettes

Visualise a named palette with `print_palette()`:

```{r vis_palettes, fig.width=14, fig.height=3, dpi=400}
print_palette(name = "bodied")
print_palette(name = "esther")
print_palette(name = "glue")
print_palette(name = "hotbot")
print_palette(name = "ibrik")
print_palette(name = "poodle")
print_palette(name = "rush")
```

### Palette info

Print the track name, artist name and URL link for a named palette with `info()`:

```{r}
info("rush")
```

## Contributing

Please add new palettes based on your favourite records! Contributing guide coming soon! `r emo::ji("eyes")`
