---
title: "Technocolour"
author:
  - "Sophie Meakin"
date: "`r Sys.Date()`"
output:
  md_document:
    variant: markdown_github
    toc: false
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE,
                      fig.path = "man/figures/")

library(ggplot2)
devtools::load_all()

```

# technocolour: colour palettes based on electronic music records

The [`technocolour`](https://sophiemeakin.github.io/technocolour/index.html) package contains colour palettes based on the album artwork some of my favourite electronic music records. Enjoy!

## Installation

You can install the package from Github:

```{r, eval = FALSE}
devtools::install_github("sophiemeakin/technocolour")
```

## Available palettes

```{r echo = FALSE, fig.width = 14, fig.height = 6}
par(mfrow = c(ceiling(length(list_palettes())/4), 4))
print_palette(name = "bodied")
print_palette(name = "esther")
print_palette(name = "hotbot")
print_palette(name = "ibrik")
print_palette(name = "poodle")
print_palette(name = "rush")
print_palette(name = "x")
par(mfrow = c(1,1))
```

## Quick-start guide

### List available palettes

List the names of all available palettes with [`list_palettes()`](https://sophiemeakin.github.io/technocolour/reference/print_palette.html); you can specify the type of palette (qualitative, sequential, or diverging) with the argument `type`:

```{r}
list_palettes()
```

### Visualise palettes

Preview a named palette with [`print_palette()`](https://sophiemeakin.github.io/technocolour/reference/print_palette.html):

```{r vis_palettes, fig.width=14, fig.height=3, dpi=400}
print_palette(name = "esther")
```

### Using with ggplot2

Use [`scale_color_techno()`](https://sophiemeakin.github.io/technocolour/reference/scale_color_techno.html) and [`scale_fill_techno()`](https://sophiemeakin.github.io/technocolour/reference/scale_fill_techno.html) to use the palette in ggplot object:

```{r example1, fig.width = 12, fig.height = 6, dpi = 400}

ggplot(data = iris,
       aes(x = Petal.Length, y = Petal.Width, col = Species)) +
  geom_point(size = 3) +
  scale_color_techno(name = "rush") +
  theme_bw() +
  theme(legend.position = "top",
        text = element_text(size = 14))

```

### Palette info

Print the track name, artist name and URL link for a named palette with [`info()`](https://sophiemeakin.github.io/technocolour/reference/info.html):

```{r}
info("poodle")
```

Please read the [package documentation](https://sophiemeakin.github.io/technocolour/reference/index.html) for full details of how to use package.

## Contributing

Please add new palettes based on your favourite records! Contributing guide coming soon! `r emo::ji("eyes")`
